\textbf{Transparency to hybrid open access through publisher-provided metadata: An article-level study of Elsevier}

### 2021-05-09 analysis/manuscript.Rmd
group field per subject area, consider also to provide percentages per subject area

make_pal <- scales::col_numeric(
  palette  = c("white", "#fcde9c","#faa476","#f0746e","#e34f6f","#dc3977"),
  na.color = "#808080",
  domain = NULL,
  alpha = FALSE,
  reverse = FALSE
)

funder_overview_subject %>%
  mutate_at(3:6, function(x){
    round(x*100,0)
  }) %>%
  mutate_at(3:6, function(x){
    cell_spec(x, background = make_pal(x))}) %>%
  kbl(booktabs = TRUE, "latex", format.args = list(big.mark = ","), digits = 1, escape = FALSE,
                  caption = "Invoice channels by discipline 2015-2019.",
                  position = "H",
      col.names = c("Subject", "OA articles", "Author", "Agreement", "Fee waived", "Other"),
       linesep = "",
      align = "lrrrrr") %>%
  add_header_above(c(" " = 2, "Invoice channel (in %)" = 4)) %>%
  kable_styling(latex_options = c("scale_down"))
```

>>>>

# define heat-colors
make_pal <- scales::col_numeric(
  palette  = c("white", "#fcde9c","#faa476","#f0746e","#e34f6f","#dc3977"),
  na.color = "#808080",
  domain = NULL,
  alpha = FALSE,
  reverse = FALSE
)
# prepare row-wise grouping per subject area
subject_table <- jn_subjects %>% 
  distinct(subject_area, top_level) %>%
  inner_join(funder_overview_subject, by = "top_level") %>%
  mutate_at(4:7, function(x){
    round(x*100,0)
  }) %>%
  mutate_at(4:7, function(x){
    cell_spec(x, background = make_pal(x))}) %>%
  mutate_at(3, function(x){
    cell_spec(x, background = make_pal(x))})

subject_table %>%
  group_by(subject_area) %>%
  arrange(top_level, .by_group = TRUE) %>% 
  ungroup() %>%
  select(-subject_area) %>%
            kbl(booktabs = TRUE, "latex", format.args = list(big.mark = ","), digits = 1, escape = FALSE,
                  caption = "Invoice channels by discipline 2015-2019.",
                  position = "H",
      col.names = c("Subject", "OA articles", "Author", "Agreement", "Fee waived", "Other"),
       linesep = "",
      align = "lrrrrr") %>%
  add_header_above(c(" " = 2, "Invoice channel (in %)" = 4)) %>%
  # manual, puh, not good 
  pack_rows("Health Sciences", 1, 5) %>%
  pack_rows("Life Sciences", 6, 10) %>%
  pack_rows("Health Sciences", 11, 20) %>%
  pack_rows("Health Sciences", 21, 26) %>%
  kable_styling(latex_options = c("scale_down"))
```

### 2021-05-09 analysis/manuscript.tex
group field per subject area, consider also to provide percentages per subject area

Nursing & 1,504 & \cellcolor[HTML]{DC3977}{82} & \cellcolor[HTML]{FFFFFF}{16} & \cellcolor[HTML]{FFF7E8}{1} & \cellcolor[HTML]{FCDE9C}{1}\\
Decision Sciences & 785 & \cellcolor[HTML]{E6576F}{72} & \cellcolor[HTML]{FCC088}{27} & \cellcolor[HTML]{FFFFFF}{0} & \cellcolor[HTML]{FCDE9C}{1}\\
Pharmacology, Toxicology and Pharmaceutics & 4,075 & \cellcolor[HTML]{EA646F}{69} & \cellcolor[HTML]{FCC088}{27} & \cellcolor[HTML]{FFF7E8}{1} & \cellcolor[HTML]{FAA476}{2}\\
Business, Management and Accounting & 1,751 & \cellcolor[HTML]{EC686E}{68} & \cellcolor[HTML]{FBAF7D}{29} & \cellcolor[HTML]{FFF0D2}{2} & \cellcolor[HTML]{FCDE9C}{1}\\
Dentistry & 288 & \cellcolor[HTML]{EC686E}{68} & \cellcolor[HTML]{FFFAF1}{17} & \cellcolor[HTML]{F89774}{10} & \cellcolor[HTML]{DC3977}{5}\\
Health Professions & 674 & \cellcolor[HTML]{ED6D6E}{67} & \cellcolor[HTML]{FCD898}{24} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{DC3977}{5}\\
Medicine & 23,623 & \cellcolor[HTML]{F0756E}{65} & \cellcolor[HTML]{FCD092}{25} & \cellcolor[HTML]{FCC98E}{6} & \cellcolor[HTML]{E34F6F}{4}\\
Agricultural and Biological Sciences & 7,956 & \cellcolor[HTML]{F38170}{63} & \cellcolor[HTML]{F9A075}{31} & \cellcolor[HTML]{FCD697}{5} & \cellcolor[HTML]{FCDE9C}{1}\\
Computer Science & 3,185 & \cellcolor[HTML]{F38170}{63} & \cellcolor[HTML]{F27F70}{36} & \cellcolor[HTML]{FFFFFF}{0} & \cellcolor[HTML]{FCDE9C}{1}\\
Economics, Econometrics and Finance & 2,071 & \cellcolor[HTML]{F48771}{62} & \cellcolor[HTML]{F79373}{33} & \cellcolor[HTML]{FCD697}{5} & \cellcolor[HTML]{FFFFFF}{0}\\
Veterinary & 2,091 & \cellcolor[HTML]{F58D72}{61} & \cellcolor[HTML]{FCD092}{25} & \cellcolor[HTML]{F1766E}{13} & \cellcolor[HTML]{FCDE9C}{1}\\
Social Sciences & 6,306 & \cellcolor[HTML]{F79273}{60} & \cellcolor[HTML]{F27F70}{36} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{FFFFFF}{0}\\
Earth and Planetary Sciences & 4,532 & \cellcolor[HTML]{F89874}{59} & \cellcolor[HTML]{F48671}{35} & \cellcolor[HTML]{FCD697}{5} & \cellcolor[HTML]{FFFFFF}{0}\\
Biochemistry, Genetics and Molecular Biology & 15,903 & \cellcolor[HTML]{F89874}{59} & \cellcolor[HTML]{F48671}{35} & \cellcolor[HTML]{FDE1A5}{4} & \cellcolor[HTML]{FAA476}{2}\\
Immunology and Microbiology & 5,542 & \cellcolor[HTML]{F89874}{59} & \cellcolor[HTML]{F58D72}{34} & \cellcolor[HTML]{FCC98E}{6} & \cellcolor[HTML]{FAA476}{2}\\
Environmental Science & 9,000 & \cellcolor[HTML]{F99D75}{58} & \cellcolor[HTML]{EF726E}{38} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{FCDE9C}{1}\\
Psychology & 3,087 & \cellcolor[HTML]{FAA376}{57} & \cellcolor[HTML]{EC686E}{40} & \cellcolor[HTML]{FFF0D2}{2} & \cellcolor[HTML]{FCDE9C}{1}\\
Neuroscience & 5,906 & \cellcolor[HTML]{FBAA7A}{56} & \cellcolor[HTML]{EC686E}{40} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{FCDE9C}{1}\\
Arts and Humanities & 1,565 & \cellcolor[HTML]{FCB882}{54} & \cellcolor[HTML]{E4536F}{44} & \cellcolor[HTML]{FFF7E8}{1} & \cellcolor[HTML]{FFFFFF}{0}\\
Mathematics & 2,105 & \cellcolor[HTML]{FCBF87}{53} & \cellcolor[HTML]{EF726E}{38} & \cellcolor[HTML]{FBAF7D}{8} & \cellcolor[HTML]{FFFFFF}{0}\\
Engineering & 8,405 & \cellcolor[HTML]{FCD395}{50} & \cellcolor[HTML]{E24C70}{46} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{FCDE9C}{1}\\
Materials Science & 4,838 & \cellcolor[HTML]{FCDA99}{49} & \cellcolor[HTML]{E14971}{47} & \cellcolor[HTML]{FDE1A5}{4} & \cellcolor[HTML]{FFFFFF}{0}\\
Chemistry & 4,033 & \cellcolor[HTML]{FCE0A1}{48} & \cellcolor[HTML]{E24C70}{46} & \cellcolor[HTML]{FCD697}{5} & \cellcolor[HTML]{FCDE9C}{1}\\
Energy & 4,286 & \cellcolor[HTML]{FEE7B8}{46} & \cellcolor[HTML]{DC3977}{52} & \cellcolor[HTML]{FFF7E8}{1} & \cellcolor[HTML]{FCDE9C}{1}\\
Chemical Engineering & 2,977 & \cellcolor[HTML]{FFEBC4}{45} & \cellcolor[HTML]{E14971}{47} & \cellcolor[HTML]{FCBC85}{7} & \cellcolor[HTML]{FCDE9C}{1}\\
Physics and Astronomy & 5,859 & \cellcolor[HTML]{FFFFFF}{40} & \cellcolor[HTML]{EF726E}{38} & \cellcolor[HTML]{DC3977}{22} & \cellcolor[HTML]{FFFFFF}{0}\\

>>>>

\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Health Sciences}}\\
\hspace{1em}Dentistry & \cellcolor[HTML]{FFFFFF}{288} & \cellcolor[HTML]{EC686E}{68} & \cellcolor[HTML]{FFFAF1}{17} & \cellcolor[HTML]{F89774}{10} & \cellcolor[HTML]{DC3977}{5}\\
\hspace{1em}Health Professions & \cellcolor[HTML]{FFFCF7}{674} & \cellcolor[HTML]{ED6D6E}{67} & \cellcolor[HTML]{FCD898}{24} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{DC3977}{5}\\
\hspace{1em}Medicine & \cellcolor[HTML]{DC3977}{23623} & \cellcolor[HTML]{F0756E}{65} & \cellcolor[HTML]{FCD092}{25} & \cellcolor[HTML]{FCC98E}{6} & \cellcolor[HTML]{E34F6F}{4}\\
\hspace{1em}Nursing & \cellcolor[HTML]{FFF6E5}{1504} & \cellcolor[HTML]{DC3977}{82} & \cellcolor[HTML]{FFFFFF}{16} & \cellcolor[HTML]{FFF7E8}{1} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Veterinary & \cellcolor[HTML]{FFF2D9}{2091} & \cellcolor[HTML]{F58D72}{61} & \cellcolor[HTML]{FCD092}{25} & \cellcolor[HTML]{F1766E}{13} & \cellcolor[HTML]{FCDE9C}{1}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Life Sciences}}\\
\hspace{1em}Agricultural and Biological Sciences & \cellcolor[HTML]{FCB983}{7956} & \cellcolor[HTML]{F38170}{63} & \cellcolor[HTML]{F9A075}{31} & \cellcolor[HTML]{FCD697}{5} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Biochemistry, Genetics and Molecular Biology & \cellcolor[HTML]{EC686E}{15903} & \cellcolor[HTML]{F89874}{59} & \cellcolor[HTML]{F48671}{35} & \cellcolor[HTML]{FDE1A5}{4} & \cellcolor[HTML]{FAA476}{2}\\
\hspace{1em}Immunology and Microbiology & \cellcolor[HTML]{FCD797}{5542} & \cellcolor[HTML]{F89874}{59} & \cellcolor[HTML]{F58D72}{34} & \cellcolor[HTML]{FCC98E}{6} & \cellcolor[HTML]{FAA476}{2}\\
\hspace{1em}Neuroscience & \cellcolor[HTML]{FCD294}{5906} & \cellcolor[HTML]{FBAA7A}{56} & \cellcolor[HTML]{EC686E}{40} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Pharmacology, Toxicology and Pharmaceutics & \cellcolor[HTML]{FEE4AF}{4075} & \cellcolor[HTML]{EA646F}{69} & \cellcolor[HTML]{FCC088}{27} & \cellcolor[HTML]{FFF7E8}{1} & \cellcolor[HTML]{FAA476}{2}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Health Sciences}}\\
\hspace{1em}Chemical Engineering & \cellcolor[HTML]{FFECC6}{2977} & \cellcolor[HTML]{FFEBC4}{45} & \cellcolor[HTML]{E14971}{47} & \cellcolor[HTML]{FCBC85}{7} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Chemistry & \cellcolor[HTML]{FEE4AF}{4033} & \cellcolor[HTML]{FCE0A1}{48} & \cellcolor[HTML]{E24C70}{46} & \cellcolor[HTML]{FCD697}{5} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Computer Science & \cellcolor[HTML]{FFEAC1}{3185} & \cellcolor[HTML]{F38170}{63} & \cellcolor[HTML]{F27F70}{36} & \cellcolor[HTML]{FFFFFF}{0} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Earth and Planetary Sciences & \cellcolor[HTML]{FDE1A5}{4532} & \cellcolor[HTML]{F89874}{59} & \cellcolor[HTML]{F48671}{35} & \cellcolor[HTML]{FCD697}{5} & \cellcolor[HTML]{FFFFFF}{0}\\
\hspace{1em}Energy & \cellcolor[HTML]{FDE3AA}{4286} & \cellcolor[HTML]{FEE7B8}{46} & \cellcolor[HTML]{DC3977}{52} & \cellcolor[HTML]{FFF7E8}{1} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Engineering & \cellcolor[HTML]{FBB380}{8405} & \cellcolor[HTML]{FCD395}{50} & \cellcolor[HTML]{E24C70}{46} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Environmental Science & \cellcolor[HTML]{FBAC7B}{9000} & \cellcolor[HTML]{F99D75}{58} & \cellcolor[HTML]{EF726E}{38} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Materials Science & \cellcolor[HTML]{FCDF9E}{4838} & \cellcolor[HTML]{FCDA99}{49} & \cellcolor[HTML]{E14971}{47} & \cellcolor[HTML]{FDE1A5}{4} & \cellcolor[HTML]{FFFFFF}{0}\\
\hspace{1em}Mathematics & \cellcolor[HTML]{FFF2D8}{2105} & \cellcolor[HTML]{FCBF87}{53} & \cellcolor[HTML]{EF726E}{38} & \cellcolor[HTML]{FBAF7D}{8} & \cellcolor[HTML]{FFFFFF}{0}\\
\hspace{1em}Physics and Astronomy & \cellcolor[HTML]{FCD394}{5859} & \cellcolor[HTML]{FFFFFF}{40} & \cellcolor[HTML]{EF726E}{38} & \cellcolor[HTML]{DC3977}{22} & \cellcolor[HTML]{FFFFFF}{0}\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Health Sciences}}\\
\hspace{1em}Arts and Humanities & \cellcolor[HTML]{FFF6E4}{1565} & \cellcolor[HTML]{FCB882}{54} & \cellcolor[HTML]{E4536F}{44} & \cellcolor[HTML]{FFF7E8}{1} & \cellcolor[HTML]{FFFFFF}{0}\\
\hspace{1em}Business, Management and Accounting & \cellcolor[HTML]{FFF4E0}{1751} & \cellcolor[HTML]{EC686E}{68} & \cellcolor[HTML]{FBAF7D}{29} & \cellcolor[HTML]{FFF0D2}{2} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Decision Sciences & \cellcolor[HTML]{FFFBF4}{785} & \cellcolor[HTML]{E6576F}{72} & \cellcolor[HTML]{FCC088}{27} & \cellcolor[HTML]{FFFFFF}{0} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Economics, Econometrics and Finance & \cellcolor[HTML]{FFF2D9}{2071} & \cellcolor[HTML]{F48771}{62} & \cellcolor[HTML]{F79373}{33} & \cellcolor[HTML]{FCD697}{5} & \cellcolor[HTML]{FFFFFF}{0}\\
\hspace{1em}Psychology & \cellcolor[HTML]{FFEBC3}{3087} & \cellcolor[HTML]{FAA376}{57} & \cellcolor[HTML]{EC686E}{40} & \cellcolor[HTML]{FFF0D2}{2} & \cellcolor[HTML]{FCDE9C}{1}\\
\hspace{1em}Social Sciences & \cellcolor[HTML]{FCCD91}{6306} & \cellcolor[HTML]{F79273}{60} & \cellcolor[HTML]{F27F70}{36} & \cellcolor[HTML]{FFE8BB}{3} & \cellcolor[HTML]{FFFFFF}{0}\\
